Appendix

### 2024-07-03 manuscript/manuscript.Rmd
WIP on the discussion.

In their work on power transformation, Box and Cox already mention transformation with a shift parameter, but preferred the version in Eq. **INSERT REFERENCE** for the theoretical analysis in their paper [@Box1964-mz], which subsequently became the convention. Yeo and Johnson's power transformation lacks a shift parameter altogether [@Yeo2000-vw].
We showed that these power transformations are sensitive to location and scale of data distributions.
To mitigate this issue, we defined location- and scale-invariant variants of the Box-Cox and Yeo-Johnson transformations.
We furthermore assessed methods for making these transformations robust to outliers, and devised an empirical test for central normality.
We showed that Conventional transformations The location- and scale-invariant transformations removed the effect of location shifts away from 0 and scaling away from 1 on estimation of the transformation parameter $\lambda$.

We investigated the use of robust invariant power transformation as part of the machine learning process, and did not find a major positive or negative effect compared to conventional transformations. A possible explanation is that numeric features with large location shifts ($|\mu| > 1000.0$) were uncommon. Of the 4886 numeric features in the 232 datasets with numeric features, 266 (5%) features in 34 datasets had large location shifts, of which 200 appeared in just 2 datasets.

>>>>

In their work on power transformation, Box and Cox already mention transformation with a shift parameter, but preferred the version in Eq. \ref{eqn:box-cox-original} for the theoretical analysis in their paper [@Box1964-mz], which subsequently became the convention.
Yeo and Johnson's power transformation lacks a shift parameter altogether [@Yeo2000-vw].
We showed that these power transformations are sensitive to location and scale of data distributions.
To mitigate this issue, we defined location- and scale-invariant variants of the Box-Cox and Yeo-Johnson transformations.
We furthermore assessed methods for making these transformations robust to outliers, and devised an empirical test for central normality.

Robust location- and scale-invariant transformations form a suitable replacement for their conventional counterparts.
They demonstrated robustness against outliers and prevent inaccurate transformations and potential numerical issues due to location and scale of the data distribution.
This is particularly relevant for automated data processing, where such issues may go unnoticed.
However, we did not find a measurable benefit for -- nor detriment to -- model performance in a machine learning experiment of 232 real-world datasets that contained at least one numeric variable.
One reason may be that numeric features with large location shifts ($|\mu| > 1000.0$) were uncommon.
Of the 4886 numeric variables in the 232 datasets, 266 (5%) variables in 34 datasets had large location shifts, of which 200 appeared in just 2 datasets.

Robust location- and scale-invariant transformations are realised by simultaneously optimising three parameters, i.e. transformation parameter $\lambda$, shift parameter $x_0$ and scale parameter $s$, using maximum likelihood optimisation.
It is feasible that standardisation of a numeric variable (e.g., through subtracting its median value and division by its interquartile range) prior to conventional transformations may achieve a similar effect in mitigating sensitivity to the distribution's location and scale.

### 2024-07-03 manuscript/manuscript_appendix.Rmd
WIP on the discussion.

Location and scale-invariant Box-Cox and Yeo-Johnson transformations are parameterised using location $x_0$ and scale $s$ parameters, in addition to transformation parameter $\lambda$.
This leads to the following transformations. The location and scale-invariant Box-Cox transformation is:

>>>>

Location and scale-invariant Box-Cox and Yeo-Johnson transformations are parametrised using location $x_0$ and scale $s$ parameters, in addition to transformation parameter $\lambda$.
This leads to the following transformations. The location and scale-invariant Box-Cox transformation is:
